Scoring_questionnaires2021

### 2022-02-07 Questionnaires_scoring2021.Rmd
07 Jan return

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/data_exp_11458-v9 (2)/Select")

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/AQ")
# 345_356
read_selfrep1 <- function(flnm) {
    read_excel(flnm) %>%
        mutate(filename = flnm)
}

db_AQ <- list.files(pattern = "*.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep1(.))

db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")

@@

library(tidyverse)
colnames(db_AQ)

db_AQ1<- db_AQ%>%
  select(c(16,33:132))

@@

db_AQ2<- db_AQ1%>%
select(seq(1, 101, 2))

@@

@@

@@

@@

library(readxl)
db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")

@@

library(tidyverse)
colnames(db_TAS)

@@

```{r}
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

@@

library(readr)
db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")

("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")

@@

colnames(db_DASS)
db_DASS1<- db_DASS%>%
  select(c(12,13,16,32:74))

colnames(db_DASS1)

db_DASS2<- db_DASS1%>%
select(c(1:3,seq(4, 44, 2)))

@@

db_DASS4<- select(db_DASS3, c(1:2,29,25:28))
db_DASS4

@@

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/
```{r eval=FALSE, include=FALSE}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)

@@

@@

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}
library(readxl)
db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
View(data_exp_11458_v9_questionnaire_bbc4)

@@

@@

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

db_BVAQ <- list.files(pattern = "*-83b1.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

@@

@@

@@

@@

db_age <- list.files(pattern = "*-8zto.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

# db_age <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8zto-4489770.xlsx")

db_vision <- list.files(pattern = "*-8nsp.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

library(readxl)

# db_vision <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8nsp-4489770.xlsx")

db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

@@

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,35,36))

@@

@@

db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))%>%
  subset(!is.na(`Participant Private ID`))

@@

Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")

@@

db_IQ <- list.files(pattern = "*-esh8.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_IQ)

db_IQ1<- select(db_IQ, c(1,13,16, 37,40:44))

@@

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,9,8))

@@

```{r}
db_demog$`Participant Completion Code`<- NULL

db_demog$completion_code<- db_demog$`Participant Completion Code`

@@

db_self_rep <- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))

db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)

db_self_rep
write_csv(db_self_rep, "db_self_rep_345_356.csv")

write_csv(db_self_rep, "db_self_rep_350.csv")

@@

merge 
```{r}

db_self_rep
library(readr)
db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
# View(db_self_rep_350_1)

@@

db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
colnames(db_self_rep_345_356)

db_self_rep_345_356<- db_self_rep_345_356[,c(1:22)]

write_csv(db_self_rep, "db_self_rep_345_356_final.csv")
```

>>>>

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")

@@

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/AQ")
# 345_356
read_selfrep1 <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

# lvevkz = 356
db_aq_356<- subset(db_AQ, `Participant Completion Code` == "lvevkz")

db_AQ_backup<- db_AQ

db_AQ <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep1(.))

# db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")

unique(db_AQ$`Participant Completion Code`)
unique(db_AQ$`Participant Public ID`)

@@

library(tidyverse)
colnames(db_AQ)
colnames(db_aq_356)

db_AQ<- bind_rows(db_AQ, db_aq_356)

colnames(db_AQ)

db_AQ$completion_code<- db_AQ$`Participant Completion Code`

db_AQ1<- db_AQ%>%
  select(c(18,34:133))

@@

# selecting quqntised
db_AQ2<- db_AQ1%>%
select(seq(1, 101, 2))

colnames(db_AQ2)

@@

aq_labels<-paste(prefix, AQ_counter, sep = "")

# generate odd numbers to match the columns we wnt to keep
names<- c("completion_code", aq_labels)

@@

db_AQ4

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/356_557_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

@@

db_TAS_backup<- db_TAS
db_TAS_356<- subset(db_TAS, `Participant Completion Code` == "lvevkz")

db_TAS <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

library(readxl)
# db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")

@@

library(tidyverse)
colnames(db_TAS)
colnames(db_TAS_356)
db_TAS<- bind_rows(db_TAS, db_TAS_356)

@@

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/356_357_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_DASS_backup<- db_DASS
unique(db_DASS$`Participant Completion Code`)
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

@@

# db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
# 
# ("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")

@@

db_DASS<-  bind_rows(db_DASS, db_DASS_356)

colnames(db_DASS)

db_DASS1<- db_DASS%>%
  select(c(14,15,18,34:74))

colnames(db_DASS1)
db_DASS1$`Repeat Key`<- NULL

db_DASS1$completi

db_DASS2<- db_DASS1%>%
select(c(1:3,seq(4, 44, 2)))
colnames(db_DASS2)

@@

db_DASS4<- select(db_DASS3, c(1:2,29,25:29))
db_DASS4

@@

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r eval=FALSE, include=FALSE}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)

@@

db_TAS_backup$`Participant Private ID`[db_TAS_backup$`Participant Completion Code` == "lvevkz"]

db_IAS_356<- subset(db_IAS, db_IAS$`Participant Private ID` == 4520106)
db_IAS_backup<- db_IAS

# library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/356_357_611_616/356_357_611_616All_scores_ias_2021-09-13.csv")
View(db_IAS)
```

@@

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r}
# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/356_357_611_616")

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}
library(readxl)
# db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
# View(data_exp_11458_v9_questionnaire_bbc4)

@@

db_BPQ_backup<- db_BPQ
db_BPQ_356<- subset(db_BPQ, db_BPQ$completion_code == "lvevkz")

@@

db_BPQ_356$`Event Index`<- as.character(db_BPQ_356$`Event Index`)
db_BPQ<- bind_rows(db_BPQ, db_BPQ_356)

@@

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

```{r}
# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1/356_357_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_BVAQ_backup<- db_BVAQ

db_BVAQ_356<- subset(db_BVAQ, db_BVAQ$completion_code == "lvevkz")

db_BVAQ <- list.files(pattern = "*-83b1.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

@@

db_BVAQ<- bind_rows(db_BVAQ, db_BVAQ_356)

@@

colnames(db_BVAQ1)

@@

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

@@

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_age_backup<- db_age

db_age_356<- subset(db_age, db_age$`Participant Completion Code` == "lvevkz")

db_age <- list.files(pattern = "*-8zto.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_age<- bind_rows(db_age, db_age_356)

# db_age <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8zto-4489770.xlsx")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/vision8nsp")

db_vision_backup<- db_vision
db_vision_356<- subset(db_vision, db_vision$`Participant Completion Code` == "lvevkz")

db_vision <- list.files(pattern = "*-8nsp.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_vision<- bind_rows(db_vision, db_vision_356)

# db_vision <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8nsp-4489770.xlsx")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/vision8nsp")
db_mhealth_backup<- db_mhealth

db_mhealth_356<- subset(db_mhealth,db_mhealth$`Participant Completion Code` == "lvevkz")

db_mhealth <- list.files(pattern = "*-v2gn.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_mhealth$`mental_health-text`<- as.character(db_mhealth$`mental_health-text`)
db_mhealth<- bind_rows(db_mhealth, db_mhealth_356)

@@

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,35,36))
db_age1<- subset(db_age1, db_age1$`Event Index` == 1)
db_vision1<- subset(db_vision, db_vision$`Event Index` == 1)
db_mhealth1<- subset(db_mhealth, db_mhealth$`Event Index` == 1)

@@

colnames(db_mhealth1)

@@

colnames(db_vision1)

# db_age1<- select(db_age, c(1,13,16,35,36))
db_age1<- subset(db_age1, db_age1$`Event Index` == 1)
db_vision1<- subset(db_vision1, db_vision1$`Event Index` == 1)
db_mhealth1<- subset(db_mhealth1, db_mhealth1$`Event Index` == 1)

# note this is ignoring the last
db_demog <- left_join(db_vision1, db_mhealth1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))

db_demog <- left_join(db_demog,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))

@@

Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r}
# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8/356_357_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

@@

db_IQ_backup<- db_IQ

db_IQ_356<- subset(db_IQ, db_IQ$`Participant Completion Code` =="lvevkz" )
colnames(db_IQ1)
db_IQ <- list.files(pattern = "*-esh8.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_IQ)
iqnames<- colnames(db_IQ1)
# db_IQ1<- select(db_IQ, c(1,12,15, 35,38:44))
db_IQ1<- select(db_IQ, iqnames)

@@

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,7,6))

@@

db_demog$completion_code <- db_demog$`Participant Completion Code`
db_demog$`Participant Completion Code`<- NULL

@@

db_self_rep_backup<- db_self_rep

db_AQ4
# db_demog has priovate and code
db_code_private<- select(db_demog, c(completion_code, `Participant Private ID`))
db_IAS<- left_join(db_IAS,db_code_private, by = "completion_code")

# merge all side by side based on a comoon column
db_self_rep_temp<- left_join(db_demog, db_DASS4, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_TAS4, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_AQ4, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_BVAQ3, by = "completion_code")

db_self_rep_temp<- left_join(db_self_rep_temp, db_IQ4, by = "completion_code")

db_self_rep_temp<- left_join(db_self_rep_temp, db_BPQ3, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_IAS, by = "completion_code")

# db_self_rep <- Reduce(merge, list(db_demog$completion_code,db_DASS4,db_TAS4$completion_code, db_AQ4$completion_code, db_BVAQ3$completion_code, db_IQ4$completion_code, db_BPQ3,db_IAS$`Participant Private ID`))

db_demog
# db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)
db_self_rep_backup<- db_self_rep
db_self_rep<- db_self_rep_temp

db_self_rep
# write_csv(db_self_rep, "db_self_rep_345_356.csv")

# write_csv(db_self_rep, "db_self_rep_350.csv")

write_csv(db_self_rep, "db_self_rep_356_367_611_616.csv")

@@

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r}
# STAI_T:: 5nzr

# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr/356_356_611_616")

# STAIS: 8rfo

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

library(readxl)
db_STAI_T <- read_excel("data_exp_11458-v9_questionnaire-5nzr_345_356.xlsx")

db_STAI_T_backup<- db_STAI_T

db_STAI_T_356<- subset(db_STAI_T, db_STAI_T$completion_code == "lvevkz")

db_STAI_T<- list.files(pattern = "*-5nzr.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_STAI_T_356$`Event Index`<- as.character(db_STAI_T_356$`Event Index`)

db_STAI_T<- bind_rows(db_STAI_T, db_STAI_T_356)

# eliminate empty rows
db_STAI_T<- subset(db_STAI_T, db_STAI_T$`Event Index`== 1)

db_STAI_T$completion_code<- db_STAI_T$`Participant Completion Code`

colnames(db_STAI_T)
db_STAI_T1<- db_STAI_T %>%
    select("Participant Private ID","completion_code", 
           STAI_01:STAI_20)%>%
  # drop anything with quantised or text
  select(-contains("quantised"))

# score

colnames(db_STAI_T1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_STAI_T2<- db_STAI_T1%>%
   mutate(STAIT = rowSums(.[ 3:22]))

colnames(db_STAI_T2)
db_STAI_T3<- select(db_STAI_T2, c(1:2, 23))
db_STAI_T3

library(readxl)
# db_STAI_S <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/data_exp_11458-v9_questionnaire-8rfo_345_356.xlsx")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/356_357_611_616")

db_STAI_S_backup<- db_STAI_S

db_STAI_S_546<- subset(db_STAI_S, db_STAI_S$completion_code == "lvevkz")

db_STAI_S<- list.files(pattern = "*-8rfo.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_STAI_S_546$`Event Index`<- as.character(db_STAI_S_546$`Event Index`)

db_STAI_S<- bind_rows(db_STAI_S, db_STAI_S_546)

# eliminate empty rows
db_STAI_S <- subset(db_STAI_S, db_STAI_S$`Event Index`== 1)

db_STAI_S$completion_code<- db_STAI_S$`Participant Completion Code`

colnames(db_STAI_S)

db_STAI_S1<- db_STAI_S %>%
    select("Participant Private ID","completion_code", 
           STAIS_01:STAIS_20)%>%
  # drop anything with quantised or text
  select(-contains("quantised"))

# score

colnames(db_STAI_S1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_STAI_S2<- db_STAI_S1%>%
   mutate(STAIS = rowSums(.[ 3:22]))

colnames(db_STAI_S2)

db_STAI_S3<- select(db_STAI_S2, c(1:2, 23))
colnames(db_STAI_S3)

db_STAI<- left_join(db_STAI_S3, db_STAI_T3)

merge 
```{r}
db_self_rep
library(readr)
# db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
# View(db_self_rep_350_1)

@@

# db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
colnames(db_self_rep)

db_self_rep_345_356<- db_self_rep[,c(1:25)]

# library(readxl)
Interoception_Study_Logbook <- read_excel("Interoception Study Logbook.xlsx")

library(readxl)
Interoception_Study_Logbook <- read_excel("Interoception Study Logbook _with456_357_611_616.xlsx")
# View(Interoception_Study_Logbook_with456_357_611_616)
View(Interoception_Study_Logbook)

db_self_rep_345_356$completion_code

Interoception_Study_Logbook$completion_code

ssid<- select(Interoception_Study_Logbook, c(1:3))
ssid$completion_code<- ssid$`Completion Code`

db_self_rep_345_356<- left_join(db_self_rep_345_356,ssid, by = "completion_code")
# write_csv(db_self_rep_345_356, "db_self_rep_345_356_final.csv")
write_csv(db_self_rep_345_356, "db_self_rep_356_357_611_616_final.csv")
```

# - CHECK WASI M on the norms

db_age2<- subset(db_age1, !is.na(`Participant Private ID`))
db_age2

db_self_rep_345_356<- left_join(db_self_rep_345_356,db_age2)

db_self_rep_345_356

colnames(db_self_rep_345_356)

db_self_rep_345_356

db_self_rep_345_356<- left_join(db_self_rep_345_356, db_STAI)
